Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-30 paper/paper7/paper7.tex
evaluation

\begin{hyp}
A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible in existing constraint languages which confirms the necessity to provide suitable constraint languages.
\end{hyp} 
In general, \emph{vocabulary} and \emph{simple constraints} are easily, concisely, and intuitively expressible by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}). 
This is not the case, however, for \emph{complex constraints} which in most cases are still only expressible by plain \emph{SPARQL}. 
As almost 1/2 of all violations are caused by \emph{complex constraints}, 
data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{complex constraints} in an easy, concise, and intuitive way.
%Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.

@@

1/2 of all constraints are \emph{error constraints} and
10\% of all constraints are \emph{warning constraints}.
\emph{Informational constraints} caused 1/3 and
\emph{warning constraints} 2/3 of all violations.
As the percentage of severe violations is very low for all vocabularies,
data quality is high with regard to the severity level of constraints.

80\% of the \emph{QB} constraints are error constraints.
More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are informational constraints.
1/6 of the Disco violations are caused by error constraints.
Almost all \emph{QB} violations and 59\% of the \emph{SKOS} violations are caused by warning constraints.  
\begin{hyp}
For well-established vocabularies, data quality is high
as serious violations rarely appear.
For newly developed vocabularies, data quality is worse
as serious violations occur partially.
\end{hyp}

>>>>

\begin{hyp}
A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible in existing constraint languages which confirms the necessity to provide suitable constraint languages.
\end{hyp} 
In general, \emph{vocabulary} and \emph{simple constraints} are easily, concisely, and intuitively expressible by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}). 
This is not the case, however, for \emph{complex constraints} which in most cases are still only expressible by plain \emph{SPARQL}. 
As almost 1/2 of all violations are caused by \emph{complex constraints}, 
data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{complex constraints} in an easy, concise, and intuitive way.
%Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
1/2 of all constraints are \emph{error constraints} and
10\% of all constraints are \emph{warning constraints}.
\emph{Informational constraints} caused 1/3 and
\emph{warning constraints} 2/3 of all violations.
As the percentage of severe violations is very low for all vocabularies,
data quality is high with regard to the severity level of constraints.

@@

80\% of the \emph{QB} constraints are \emph{error constraints}.
More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are \emph{informational constraints}.
1/6 of the Disco violations are caused by \emph{error constraints} and
almost all \emph{QB} violations and 59\% of the \emph{SKOS} violations are caused by \emph{warning constraints}.  
For well-established vocabularies, data quality is high
as serious violations rarely appear.
For newly developed vocabularies, data quality is worse
as serious violations occur partially.
Constraints are serious when they violate the integrity of vocabularies.
For well-established vocabularies, it is well documented and the experience is high how to guarantee this integrity.
This is not the case or newly-developed vocabularies.
\begin{hyp}
Especially for newly developed vocabularies, constraint languages should be used to a larger extend to meet severe constraints which guarantee their integrity.   
\end{hyp}
